Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-05 paper/main.tex
Updates

\subsection{Measures of Conditional Association}
Our proposed method for iterative DAG construction relies on a measure of
conditional association, also commonly known as partial association, between
variables. Specifically, we are interested in quantifying the association
between variables $ X $ and $ Y $ when conditioned on a set of variables $
\bm{Z} $, which may be empty ($ \bm{Z} = \emptyset $). Various measures of
conditional association have been used in the literature, depending on the type
of $ X $, $ Y $, and $ \bm{Z} $. These measures are often based on the effect
size of the CI test $ X \ci Y \rvert \bm{Z} $. In this section, we provide an
overview of some of the commonly used measures for different data types.

>>>>

\subsection{Measures of Conditional Association}
Our approach for ranking CI tests is based on a measure of conditional
association -- also known as partial association -- between variables.
Specifically, we are interested in quantifying the association between
variables $ X $ and $ Y $ when conditioned on a set of variables $ \bm{Z} $
(which may be empty, i.e., $ \bm{Z} = \emptyset $). Various measures of
conditional association have been used for this purpose depending on the type
of $ X $, $ Y $, and $ \bm{Z} $. These measures are often based on the effect
size of the CI test $ X \ci Y \rvert \bm{Z} $. In this section, we give an
overview of some of the commonly used measures for different data types.
